NGO Analysis: `r params$title`

### 2022-07-25 Shiny/Test/report.Rmd
Errant character.

## Currency caption-----------------------------------------------------------s
# Fake currency caption
currency_caption <- ifelse(length(unique(htmldata$valutakode)) == 1,
  "Note: not all values are denominated in the same currency.", ""
)
# Real currency caption
# currency_caption <- ifelse(length(unique(htmldata$valutakode)) == 1,
#       "", "Note: not all values are denominated in the same currency.\n"
#     )
```

>>>>

## Currency caption-----------------------------------------------------------
# Fake currency caption
currency_caption <- ifelse(length(unique(htmldata$valutakode)) == 1,
  "Note: not all values are denominated in the same currency.", ""
)
# Real currency caption
# currency_caption <- ifelse(length(unique(htmldata$valutakode)) == 1,
#       "", "Note: not all values are denominated in the same currency.\n"
#     )
```
